An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-10-31 mixedwindow.tex
Change Assumption 3 on NED size
The NED size conditions were incorrect; this commit changes them to
the right ones.

\begin{asmp}\label{a3}%
  The series $y_t$, $x_t$, and $z_t$ are NED of size $-1/2$ on either a
  strong mixing process of size $-\frac{r}{r-2}$ for $r>2$ or a uniform
  mixing process of size $-\frac{r}{2r-2}$ for $r \geq 2$. Moreover,
  $y_t$ and $\yh_{j,t+1}$, $j = 1,\dots,J$, have uniformly bounded $2 r$
  moments.
\end{asmp}

>>>>

\begin{asmp}\label{a3}%
  The series $y_t$, $x_t$, and $z_t$ are $L_2$-NED of size
  $-(r-1)/(r-2)$ for $r > 2$ on either a strong mixing process of size
  $-r/(r-2)$ or a uniform mixing process of size
  $-r/(2r-2)$. Moreover, $y_t$, $x_t$, and $\yh_{j,t}$, $j =
  1,\dots,J$, have uniformly bounded $2 r$ moments.
\end{asmp}
